Acoustic Scene Classification: \\ Supervised and Unsupervised Approaches using the Scattering Transform

### 2016-06-21 paper/structureScene.tex
more on wavelets

\subsection{Temporal scattering}
Let $\boldsymbol{\psi}(t)$ a complex-valued band-pass filter of
dimensionless frequency $1$ and bandwidth $1/Q$.
A filter bank of wavelets is built by dilating $\boldsymbol{\psi}$
according to a geometric sequence of scales $2^{-\gamma_1/Q}$,
where the variable $\gamma$ takes integer values.
\begin{equation}
\boldsymbol{\psi_{\gamma_1}}(t) = 2^{-\gamma_1/Q} \boldsymbol{\psi}(-2^{\gamma_1/Q} t)
\end{equation}
We denote by $\boldsymbol{\psi_{\gamma_1}}(t)$ the resulting wavelets.

>>>>

\subsection{Temporal scattering}
Let $\boldsymbol{\psi}(t)$ a complex-valued band-pass filter of
dimensionless frequency $1$ and bandwidth $1/Q_1$.
A filter bank of wavelets is built by dilating $\boldsymbol{\psi}(t)$
according to a geometric sequence of temporal scales $2^{-\gamma_1/Q_1}$.
The variable $\gamma_1$, akin to a log-frequency, takes integer values between $0$ and $(J_1 \times Q_1 - 1)$.
In the sequel, the number of filters per octave $Q_1$ is set to $8$, and
the number of octaves $J_1$ is set to $10$, \ie the full audible range.
We denote by
\begin{equation}
\boldsymbol{\psi_{\gamma_1}}(t) = 2^{-\gamma_1/Q_1} \boldsymbol{\psi}(-2^{\gamma_1/Q_1} t)
\end{equation}
the wavelets resulting from the dilation of $\boldsymbol{\psi}$(t).
For some $\gamma_1$, the wavelet $\boldsymbol{\psi_{\gamma_1}}(t)$
has a center frequency of $2^{-\gamma_1/Q_1}$, a bandwidth of $2^{-\gamma_1/Q_1}/Q_1$, and a quality factor of $Q_1$.
